---
title: "Lung Cancer"
author: "KZ"
date: '2022-06-15'
output: html_document
---

This project will use the lung cancer dataset to create demographic summarise tables using the package from TableOne, with a main focus on stage 4 patient and also the immunotherapy.

### Loading Packages and Dataset
Pacman is very useful package for loading and installing the multiple packages;
Note - **there is no package called `googlesheets`**.

```{r packages, include=FALSE}
#install.packages(c("pacman"))
library(pacman)
pacman::p_load(tableone,survival,stargazer,install=TRUE)
pacman::p_load(RPostgreSQL,plyr,dplyr,tidyr,reshape2,
               #googlesheets,
               data.table,openxlsx,googledrive,Hmisc,
               stringr,stringi,bigrquery,googlesheets4,
               comorbidity,tidyverse,
               install = TRUE)
```

### Loading the Lung Cancer dataset
This part will initialize the dataset from Google Drive folder, where the folder path about output and csv might need to be updated;
The output path should direct the generated files to the folder you want to save, and the csv path should direct to the folder saving all the data files.
```{r data accessing, include=FALSE, echo=FALSE}
bq_auth(email=TRUE)
drive_auth(email = TRUE)
con <- dbConnect(bigrquery::bigquery(),  project = "bigquery-408fd9e5",  dataset = "seid")


# point to google drive folders
OUTPUT <- '1tclgDVdHQrpmCYH_pfjzHfW_LATdaYOu' #direction to the internship folder of Ke Zeng
INPUT <- as.data.frame(drive_ls(as_id('11BHDJnJ4TYY-yY012X7pgwNc5yxb-z7z')))
# assign list of input docs and SMV CSVs to data frame 
CSV <- as.data.frame(drive_ls(as_id('1MpR_0B-hfDudnrBccTvtmMxkpwPPiVce')))

### Load SMV Export ###
CSV <- subset(CSV, grepl('csv', name)) %>% arrange(name)
for (i in 1:nrow(CSV)) {  
  filename_str <- CSV$name[i]  
  temp <- drive_download(file = as_id(CSV$id[CSV$name == filename_str]), overwrite = TRUE)  
  df <- read.csv(filename_str, stringsAsFactors = F)  
  file.remove(filename_str)    
  assign(paste0(gsub('.csv', '', filename_str), '0'), df)
  }
```


```{r workbook}
# Create a blank workbook
OUTWB <- createWorkbook()
```

### Stage4 Patients
This section will firstly take a look on the whole patient stages and identify those in the stage 4.
```{r stages}
table.stages = stage0 %>% group_by(stage) %>% summarise(n=n()) %>%
   filter(str_detect(stage, "4"))
table.stages
```

We identify 4 different categories of stage 4 patients. Then we need to find these patients from the list and collect the id to know who is in stage 4.

Note - patients' characteristics of height and weight are measured multiple times with multiple time frames, so it will be difficult to get a real value.

table.a = height_weight0 %>%
  group_by(mpid,value_type) %>%
  mutate(minAccessedDate = min(assessed_timedelta)) %>%
  ungroup() %>%
  filter(assessed_timedelta == minAccessedDate) %>%
  select(mpid,value_type,standardized_value)

```{r stage4 patients}
table.patientstage4 = stage0 %>%
  filter(stage %in% table.stages$stage)

table.historyofcancer = personal_history_of_cancer0 %>% group_by(mpid) %>% mutate(ncancer = n()) %>%
  ungroup() %>%
  select(mpid,icd_code) %>%
  spread(key = c("mpid"), value= c("icd_code"))
  
  reshape(.,
          idvar = c("mpid","ncancer"),
          v.names = c("icd_code","personal_history_of_cancer_diagnosed_timedelta"),
          direction = "wide")

reshape(data = dt,
        idvar = c("Area", "Type"),
        v.names = c("Y2020", "Y2021", "Y2022"),
        timevar = "Scenario",
        direction = "wide")

table.patients4.demo = patient0 %>%
  left_join(.,tobacco_history0,by="mpid",suffix=c(".pt",".tbch")) %>%
  left_join(.,personal_history_of_cancer0,by="mpid",suffix=c(".pt",".phc")) %>%
  filter(mpid %in% table.patientstage4$mpid)
table.patients4.demo %>% head()
```
Table One on these patient demographics.
```{r patients4 tableone}
colnames(table.patients4.demo)
myVars = c("age_at_diagnosis")
catVars = c("sex","race","ethnicity","cause_of_death")
  
  
head(performance_status0)
performance_status0_1<-performance_status0%>%group_by(mpid)%>%dplyr::mutate(countm=n())
performance_status0_2<-left_join(performance_status0_1,all_patients,by='mpid')
myVars <-c("score", "method", "reported_by", "data_source", "reported_timedelta", 
           "countm")
tab2 <- CreateTableOne(vars = myVars, data = performance_status0_2, factorVars = myVars,strata = 'center')
tab3<-print(tab2, showAllLevels = TRUE,test = F,digits=1)
tab4<- as.data.frame(tab3,stringsAsFactors = F)%>%add_rownames("Name")
```

The following table shows how these patients were treated and figure out those treated by immunotherapy.
```{r patients4 regimen}
colnames(regimen0)
table.patients4.regimen = regimen0 %>%
  filter(mpid %in% table.patientstage4$mpid)
table.patients4.regimen %>% 
  filter(str_detect(regimen_name, 
                    regex("mab",ignore_case = TRUE)))
```
### Lab - Table One
This section adapts the code of creating Table One on the Lab dataframe.

#### Lab - Glance
I do not have the dataframe `all_patients`. The lab_test number is combined to the similar dataframe named `patient0`.
```{r Lab}
head(lab_test0)
colnames(lab_test0)
lab_test0_1<-lab_test0%>%group_by(mpid)%>%dplyr::mutate(countm=n())
# regimen0_2<-left_join(regimen0_1,all_patients,by='mpid')
lab_test0_2 = left_join(lab_test0_1,patient0,by='mpid')
```
#### Lab - TableOne
This section creates the table one.

```{r labTableOne}
myVars = c("quantitative_result","lab_timedelta","countm") # normal variable can be directly summarised
catVars = c("lab_name","assessed","unit","data_source") # categorical variables need transformation
tab2 <- CreateTableOne(vars = myVars, data = lab_test0_2, factorVars = catVars, strata = 'sex',test = 'F')
tab3<-print(tab2, showAllLevels = TRUE,test=F)
tab4<- as.data.frame(tab3,stringsAsFactors = F)%>%add_rownames("Name")
#write in the excel file
addWorksheet(OUTWB, "lab0")
writeData(OUTWB, sheet = "lab0", x = as.data.frame(tab4))
```

#### Lab - saving and upload
Note - you need to change the `OUTPUT` variable to the direction path you want to link
```{r saving and upload}
# Export the file
#save to google drive;
#https://drive.google.com/drive/folders/1U_erSDt-ikObDdd_lLHkoYFeMHAwOWdW
OUTPUT <- '14iIQdH8HbBAeUnJorndRWfimfUpOG7lq'

# write output to google drive
filename_str <- paste0('TableOneLab_', 
                       gsub('-', '', Sys.Date()), 
                       '.xlsx')

saveWorkbook(OUTWB,filename_str)
drive_upload(filename_str, 
             path = as_id(OUTPUT), 
             overwrite = T)
file.remove(filename_str)
```



